\fontfamily{phv}\selectfont{Causal Discovery methods for Effective Connectivity in Human Brains}

### 2014-01-17 docs/paper/paper final.tex
stukje aan de discussie toegevoegd

As can be seen in figures~\ref{assym_subjects} and~\ref{assym_avg}, the certainties of one-directional arrows are very low compared to the certainties of the bi-directional arrows. Also, the certainties of one-directional arrows are somewhat higher in EMS-PC than in standard PC. To illustrate this, the distribution of these values are presented in figure~\ref{fig:distributions}
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.49\textwidth]{images/new/dist_all_mod_blackstruct_reddir_blueantisym-crop}
  \includegraphics[width=0.49\textwidth]{images/new/dist_all_expl_blackstruct_reddir_blueantisym-crop}
  \caption{The distribution of values, for standard PC at the left, and EMS-PC at the right. The horizontal axis shows the relative number of occurences in the graph. The black line represent the distribution of results of the structural part of PC, and is equal for both variants. The red and the blue line represent the distribution of values of arrowheads and one-directional arrows, respectively.}
  \label{fig:assym_avg}
\end{figure}

@@

\section{Discussion}
%Good consistency of structure within and between subjects

@@

% Comparison Markov class standard PC and EMS-PC
Both standard PC and EMS-PC find many bi-directional arrows, with some one-directional arrows.
% TODO: find out how large these groups are.

>>>>

As can be seen in figures~\ref{assym_subjects} and~\ref{assym_avg}, the certainties of one-directional arrows are very low compared to the certainties of the bi-directional arrows. Also, the certainties of one-directional arrows are somewhat higher in EMS-PC than in standard PC. To illustrate this, the distribution of these values are presented in figure~\ref{fig:distributions}
\begin{figure}[h!]
  \centering
  \includegraphics[width=0.49\textwidth]{images/new/dist_all_mod_blackstruct_reddir_blueantisym-crop}
  \includegraphics[width=0.49\textwidth]{images/new/dist_all_expl_blackstruct_reddir_blueantisym-crop}
  \caption{The distribution of values, for standard PC at the left, and EMS-PC at the right. The horizontal axis shows the relative number of occurences in the graph. Zero-values make up more than 84\% of the graph, these are not shown in this distribution. The black line represent the distribution of results of the structural part of PC, and is equal for both variants. The red and the blue line represent the distribution of values of arrowheads and one-directional arrows, respectively.}
  \label{fig:distributions}
\end{figure}

@@

\section{Discussion}
%Good consistency of structure within and between subjects
Many structural connections found by the PC algorithm are found consistently, both within one subject and also across multiple subjects.
The connections between the two hemispheres can clearly be seen in all subjects, as well as many connections in the corpus collosum.
The consistency can also be seen in the distribution of values in figure~\ref{distributions}.
Non-zero values make up approximately 16 percentage points of the graph, of which 3 percentage points show a certainty larger than 0.5.
Approximately 1 percentage point even shows a certainty of 1.

@@

% Comparison Markov class standard PC and EMS-PC
Both standard PC and EMS-PC find many bi-directional arrows, with some one-directional arrows.
As can be seen in the distribution of values in figure~\ref{distributions}, nearly all found edges are oriented as bi-directional arrows.
For EMS-PC, this number is somewhat lower but there are still few one-directional arrows, and they do not have certainties higher than 0.15.
